### 2022-01-03 spanish/sections/editor.tex
Update editor.tex

\begin{benumerate}{2}
\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape forthcoming}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. {\itshape Pleyade}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2016). Political, Economic, and Intellectual Elites. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1). {\footnotesize \scshape [in Spanish]}. {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}} \vspace{1mm}
\end{benumerate}

>>>>

\begin{benumerate}{2}

\item{\small Gonz\'alez-Bustamante, B., \& Luci, F. ({\itshape próximamente}). Political Elites in Latin America: Socialisation, Trajectories, and Capitals. {\itshape Pléyade, Revista de Humanidades y Ciencias Sociales}.}\vspace{1mm}

\item{\small Gonz\'alez-Bustamante, B. (2016). Élites políticas, económicas e intelectuales. {\itshape Pol\'itica, Revista de Ciencia Pol\'itica, 54}(1). {\scshape url}: \href{https://revistapolitica.uchile.cl/index.php/RP/issue/view/4365}{\textcolor{blue}{https://revistapolitica.uchile.cl}}}\vspace{1mm}

\end{benumerate}
